%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

% remove the bibliography heading
\makeatletter
\renewenvironment{thebibliography}[1]
{
%     \section*{\refname}%
%      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
  \list{\@biblabel{\@arabic\c@enumiv}}%
    {\settowidth\labelwidth{\@biblabel{#1}}%
    \leftmargin\labelwidth
  \advance\leftmargin\labelsep
  \@openbib@code
  \usecounter{enumiv}%
  \let\p@enumiv\@empty
  \renewcommand\theenumiv{\@arabic\c@enumiv}}%
  \sloppy
  \clubpenalty4000
  \@clubpenalty \clubpenalty
  \widowpenalty4000%
  \sfcode`\.\@m
}
{
\def\@noitemerr
{\@latex@warning{Empty `thebibliography' environment}}%
\endlist
}
\makeatother

% multiple bibliography support
\usepackage[sorting=none, backend=biber]{biblatex} % load the package
\addbibresource{references.bib} % add a bib-reference file
% no need for ``References'' to be in front of every bibliography
\renewcommand\refname{}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section 
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Jason K.~Moore}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{2.5in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
      2408 37th St & E-mail: \href{mailto:moorepants@gmail.com}{moorepants@gmail.com}\\
      Sacramento, CA, 95817, USA &  Personal Website: \href{http://moorepants.info}{moorepants.info}\\
      +01-530-601-9791 & Linkedin: \href{http://www.linkedin.com/pub/jason-moore/40/550/322}{tinyurl.com/jkm-linkedin}\\
      & Twitter: \href{https://twitter.com/moorepants}{@moorepants}\\
      & Google+:
      \href{https://plus.google.com/110966557175293116547}{tinyurl.com/jkm-plus}
\end{tabular}

\section{Citizenship}
%
United States of America

\section{Language}
%
English [US] (mother tongue), Spanish [GU] (beginner), Dutch [NL] (beginner)

\section{Research Interests}
%
Multibody dynamics, control systems, human operator control, vehicle dynamics,
aircraft control, bicycle dynamics, aircraft dynamics, vehicle handling
qualities, human biomechanics, gait control identification, machine design,
appropriate technology, human powered machines, system identification, software
engineering, wind tunnel experimentation, computational reproducibility, open
science, optimal control

\section{Education}
%
\href{http://www.ucdavis.edu}{\textbf{University of California at Davis}},
Davis, California USA
\begin{outerlist}

\item[] Ph.D., \href{http://mae.ucdavis.edu/}{Mechanical and Aerospace
  Engineering}, August 2012
  \begin{innerlist}
    \item Dissertation:
      \href{http://moorepants.github.com/dissertation}{Human Control of A
      Bicycle}
    \item Dissertation Topic: Bicycle dynamics, control, and handling qualities
    \item Area of Study: Multibody dynamics, control systems, and system
      identification
    \item Advisors:
      \href{http://biosport.ucdavis.edu/lab-members/mont-hubbard/}{Mont~Hubbard},
      \href{http://mae.ucdavis.edu/faculty/hess/}{Ron A.~Hess},
      \href{http://bicycle.tudelft.nl/schwab/}{Arend L.~Schwab}
  \end{innerlist}

\item[] M.Sc., \href{http://mae.ucdavis.edu/}{Mechanical and Aeronautical
  Engineering}, June 2007
  \begin{innerlist}
    \item Advisor:
      \href{http://mae.ucdavis.edu/faculty/hubbard/hubbard.html}{Mont~Hubbard}
    \item Area of Study: Multibody dynamics, control systems, and machine design
  \end{innerlist}

\end{outerlist}

\blankline

\href{http://www.odu.edu}{\textbf{Old Dominion University}},
Norfolk, Virginia USA
\begin{outerlist}
\item[] B.Sc.,
        \href{http://eng.odu.edu/me/}
             {Mechanical Engineering}, December 2004
        \begin{innerlist}
        \item \emph{Magna cum Laude}
        \item Machine Design Specialization
        \item Minor in \href{http://sci.odu.edu/math/}
                            {Mathematics}
        \item Minor in \href{http://al.odu.edu/philosophy/}
                            {Philosophy and Religious Studies}
        \end{innerlist}

\end{outerlist}

\blankline

\href{http://www.pcs.k12.va.us/schools/ths/ths.htm}{\textbf{Tunstall High School}},
Dry Fork, Virginia USA
\begin{outerlist}
  \item[] Advanced Diploma, May 2000
    \begin{innerlist}
      \item Graduated with Honors
    \end{innerlist}
\end{outerlist}

\section{Professional Accreditation}
Passed the Fundamentals of Engineering Exam in Virginia

\section{Awards}
%
% TODO : Add dollar amounts to monetary awards.
%
\href{http://opensim.stanford.edu/}{Nation Center of Simulation in
  Rehabilitation Research, Stanford University}
\begin{innerlist}
  \item 2014 NCSSR Visiting Scholarship, \$8k.
\end{innerlist}

\blankline

\href{http://sagepub.com/}{SAGE Publishing}
\begin{innerlist}
  \item 2013 Best Paper Award, Journal of Multibody Dynamics, \$400.
\end{innerlist}

\blankline

\href{http://gsa.gov/}{U.S. General Services Adminstration}
\begin{innerlist}
  \item \href{http://appsforvehicles.challenge.gov/}{White House Apps for
    Vehicles Challenge: Phase 1}, 2013, \$2k.
\end{innerlist}

\blankline

\href{http://mne.psu.edu/dscc2012/}{2012 Dynamic Systems and Control Conference}
\begin{innerlist}
  \item Best paper in the Single Track Vehicle Dynamics and Control Session,
    2012.
\end{innerlist}

\blankline

\href{http://www.ucdavis.edu}{University of California, Davis}
\begin{innerlist}
  \item Summer Graduate Student Researcher Award, 2010
  \item Campus Sustainability Grant (Human Powered Utility Vehicle Pilot Program), 2008
  \item Campus Sustainability Grant (Davis Bike Church Physical Space Renovation), 2008
  \item Graduate Student Association Travel Award, 2008
  \item Institute for Transportation Studies Travel Award, 2008
  \item Campus Sustainability Grant (Pedal Powered Charging Table), 2007
  \item Joseph Beggs Fellowship for Kinematics, 2006--2007
  \item MAE Department Fellowship, UC Davis, 2005--2006
\end{innerlist}

\blankline

\href{http://www.odu.edu}{Old Dominion University}
\begin{innerlist}
  \item Governor's Technology Scholarship, Full Tuition, \$16k, 2000--2004.
\end{innerlist}
%
\section{Research Experience}
%
\href{http://csuohio.edu}{\textbf{Cleveland State University}}, Cleveland, Ohio USA
\begin{outerlist}
  \item[] \textit{Post Doctoral Research Associate}
    \hfill \textbf{July 2013 to present}
  \begin{innerlist}
    \item Identified control schemes in human walking using data driven
      approaches.
    \item Developed and ran multi-subject gait experiments with a modern gait
      lab.
    \item Developed software for gait data analysis and simulation.
    \item Developed human walking computational models.
    \item Mentored several undergraduate and graduate students in research
      projects.
    \item Mentored undergraduate students in their senior design projects.
    \item System adminstrator for the lab web site.
    \item Developed a open data paper for a very large gait dataset.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.ucdavis.edu}{\textbf{University of California at Davis}}, Davis, California USA
\begin{outerlist}
  \item[] \textit{Postdoctoral Researcher and Programmer}%
        \hfill \textbf{February 2013 to June 2013}
  \begin{innerlist}
    \item Developed a cross platform smart phone/tablet application for
      realtime automobile driver fuel economy feedback. This application was
      used to conduct an experiment with 200 drivers in San Francisco on driver
      behavior: \href{http://smartdrive.ucdavis.edu}{SmartDrive}
    \item Won \$2K in the first Phase of the White House's Apps for Vehicles
      Challenge with simpler version of SmartDrive for consumer use,
      \href{http://drive5.us}{Drive5}
    \item Designed statistical Kalman filter based fuel economy prediction
      algorithms based on smart phone sensor data.
  \end{innerlist}
  \item[] \textit{Graduate Student Researcher}%
        \hfill \textbf{September 2005 to August 2012}
  \begin{innerlist}
    \item Graduate Student Researcher at the
      \href{http://biosport.ucdavis.edu}{Sports Biomechanics Lab}.
    \item Member of UC Davis's Institute for Transportation Studies.
    \item Co-wrote and co-managed a
        \href{http://nsf.gov/awardsearch/showAward.do?AwardNumber=0928339}{three year
        Nation Science Foundation grant}.
    \item Developed a custom instrumented bicycle and performed control
        experiments to characterize the human control system in the bicycling
        balancing and tracking task.
    \item Developed numerous open source software packages.
    \item Mentored five graduate students during summer internships in
      experimental, theoretical, and computational dynamics.
    \item Mentored approximately ten undergraduate student interns in a lab
      setting.
    \item Mentored four undergraduates in their senior design project.
    \item Led multiple tours of the Sport Biomechanics Lab.
    \item Involved in the graduate student recruitment week.
    \item Designed and administered the lab website.
    \item Co-founded Davis Open Science.
    \item Co-wrote and awarded two Google Summer of Code grants (2011, 2012).
    \item Organized weekly lab meetings.
    \item Refereed an article for Vehicle System Dynamics.
    \item Organized and co-chaired both an invited and special session at the
      2012 ASME DSCC conference.
    \item Featured in ``\href{http://youtu.be/HcYbn_RCLiw}{Science of
      Balancing a Bike}'' by the UC Office of the President.
    \item Featured in ``\href{http://youtu.be/zShn5xMueso}{Science of Riding a
      Bicycle}'' video by KQED Quest.
  \end{innerlist}
  \item[] \textit{Biomedical Research Engineer}%
        \hfill \textbf{August 2007 to August 2009}
  \begin{innerlist}
    \item Designed and supervised the fabrication of a cell shearing device for
      the UCD Biomedical Passerini Lab.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.tudelft.nl}{\textbf{Delft University of Technology}}, Delft, Zuid-Holland Netherlands
\begin{outerlist}
  \item[] \textit{Fulbright Visiting Scholar and Researcher}%
        \hfill \textbf{August 2008 to August 2009}
  \begin{innerlist}
    \item Ph.D. researcher at the \href{http://bicycle.tudelft.nl}{Bicycle Dynamics Laboratory}.
    \item Co-developed an instrumented bicycle with video logging and
        accompanying software.
    \item Used the instrumented bicycle in various experiments on and off the
        treadmill resulting in two conference papers.
    \item Participated in
        \href{http://dx.doi.org/10.1126/science.1201959}{canceled gyro,
        negative trail bicycle experiments} that eventually resulted a Science
        publication.
    \item Lead motion capture study on bicycle/rider kinematics resulting in
        two conference papers and one peer reviewed journal article.
    \item Developed a systematic method of measuring the physical properties of
        a bicycle and rider resulting in two conference papers.
    \item Gave a colloquium talk on the year's research.
    \item Researched the bicycle transportation system in the Netherlands, kept
        an informal blog, attended the Velo-City Brussels conference, and gave
        a talk on the subject at the UCD Institute of Transportation Studies.
  \end{innerlist}
\end{outerlist}

\section{Grants}
%
% TODO : Add dollar amounts to monetary awards.
%
\href{http://nsf.gov/}{National Science Foundation}
\begin{innerlist}
  \item \href{http://nsf.gov/awardsearch/showAward.do?AwardNumber=0928339}{NSF
    Standard Grant: Human Control of Bicycle Dynamics with Experimental
  Validation and Implications for Bike Handling and Design}, 2009-2012, \$300k.
\end{innerlist}

\blankline

\href{http://exchanges.state.gov/}{U.S. Department of State}
\begin{innerlist}
  \item \href{http://fulbright.state.gov/}{Fulbright Grant to the Netherlands},
    2008-2009, \$10k.
\end{innerlist}

\section{Journal Publications}
\begin{refsection}
  \nocite{
    Moore2015e,
    Dembia2015,
    Schwab2013,
    Hess2012,
    Moore2011,
  }
  \printbibliography[heading=none]
\end{refsection}
%
\section{Theses}
\begin{refsection}
  \nocite{
    Moore2012
  }
  \printbibliography[heading=none]
\end{refsection}
%
\section{Preprints}
\begin{refsection}
  \nocite{
    Moore2015b,
    Moore2015a,
    Moore2014b,
    Moore2015d,
    Moore2015c,
  }
  \printbibliography[heading=none]
\end{refsection}
%
\section{Peer Reviewed Conference Proceedings}
\begin{refsection}
  \nocite{
    Moore2013a,
    Moore2013,
    Hess2013,
    Gede2013,
    Schwab2012b,
    Schwab2012a,
    Moore2010,
    Moore2010a,
    Peterson2010,
    Moore2009a,
    Kooijman2009a,
    Moore2009b,
    Moore2008,
  }
  \printbibliography[heading=none]
\end{refsection}
%
\section{Conference Abstracts}
\begin{refsection}
  \nocite{
    Moore2015,
    Moore2014c,
    Moore2007,
  }
  \printbibliography[heading=none]
\end{refsection}
\section{Software}
\begin{refsection}
  \nocite{
    Moore2014a,
    Moore2014,
    Moore2012a,
    Dembia2011,
    Moore2011a,
    Moore2011b,
    Moore2011c,
    Gede2009,
    SymPy2006
  }
\printbibliography[heading=none]
\end{refsection}
%\section{Data}
%
%\section{Posters}
% TODO : Add posters.
%
\section{Teaching Experience}
%
\href{http://www.software-carpentry.org}{\textbf{Software Carpentry}},
Everywhere, Planet Earth
\begin{outerlist}
  \item[] \textit{Volunteer Instructor}%
    \hfill \textbf{January 2015 to now}
  \begin{innerlist}
    \item Lead two workshops on computation for scientists and engineers.
    \item Developed lesson plans.
    \item Passed the instructor certification.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://csuohio.edu}{\textbf{Cleveland State University}}, Cleveland, Ohio USA
\begin{outerlist}
  \item[] \textit{Post Doctoral Research Associate}
    \hfill \textbf{July 2013 to present}
  \begin{innerlist}
    \item Mentored graduate students.
    \item Mentored undergraduate students in their senior design projects.
    \item Led ``Open Source Code Nights'' workshops with the undergraduate IEEE group.
    \item Gave tutorials on mutlibody dynamics and control to graduate and
      undergraduate students.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.ucdavis.edu}{\textbf{University of California at Davis}}, Davis, California USA
\begin{outerlist}
  \item[] \textit{Lecturer}%
        \hfill \textbf{August 2012 to December 2012}
  \begin{innerlist}
  \item Taught
    ``\href{http://mae.ucdavis.edu/~biosport/jkm/courses/eng4/}{Engineering
    Graphics in Design}'', 120 students, 4 Teaching Assistants
    \item Topics: Design, Sketching, Drawing, Drafting, Solid Modeling, CAD
  \end{innerlist}
  \item[] \textit{Graduate Student Researcher}%
        \hfill \textbf{September 2005 to August 2012}
  \begin{innerlist}
    \item Mentored five graduate students during summer internships in
      experimental, theoretical, and computational dynamics.
    \item Mentored approximately ten undergraduate student interns in a lab
      setting.
    \item Mentored four undergraduates in their senior design project.
    \item Led multiple tours of the Sport Biomechanics Lab.
  \end{innerlist}
  \item[] \textit{Machine Shop Supervisor}%
    \hfill \textbf{January 2007 to June 2008}
  \begin{innerlist}
    \item Supervised the College of Engineering student machine shop.
    \item Helped students with machining and fabrication projects.
    \item Taught the shop safety class.
    \item Fabricated various doodads and gizmos for the shop.
    \item Organized the shop.
    \item Worked on design projects for various campus research groups.
  \end{innerlist}
  \item[] \textit{Teaching Assistant}%
    \hfill \textbf{March 2006 to June 2007}
  \begin{innerlist}
    \item EME 150B, Mechanical Design (Spring 2006): Worked with student groups
        during the discussion period on their design projects, graded homework
        assignments, and held weekly office hours.
    \item EME 50, Manufacturing Processes (Fall 2006 and Winter 2007): Taught
        hands-on machining and fabrication during weekly lab sections, graded
        homework assignments and tests, and organized the end of quarter party.
    \item ENG 4, Engineering Graphics (Spring 2007): Led lab sections with
        lectures in sketching and 2D/3D computer aided design with modern CAD
        software.
  \end{innerlist}
  \item[] \textit{Davis Open Science Co-founder}%
    \hfill \textbf{February 2010 to June 2013}
  \begin{innerlist}
    \item Co-founded the graduate student group.
    \item Co-hosted several seminars and panels with prominent speakers in Open
      Science.
    \item Worked with various faculty and staff on open science projects.
    \item Led workshops on open science topics.
  \end{innerlist}
  \item[] \textit{Action Research Team Facilitator}%
        \hfill \textbf{March 2007 to December 2007}
  \begin{innerlist}
    \item Led group of students in the design and construction of a
        \href{http://mae.ucdavis.edu/~biosport/jkm/ped_desk.htm}{pedal powered
        desk laptop charging station}.
    \item Competed in Google and Specialized's Innovate or Die Contest.
    \item The project was featured in many articles and news broadcasts.
    \item Featured in the book
        \href{http://www.thehumanpoweredhome.com/}{\underline{Human Powered
        Home}} by Tamara Dean.
  \end{innerlist}
  \item[] \textit{Assistant Action Research Team Facilitator}%
    \hfill \textbf{March 2006 to June 2006}
  \begin{innerlist}
    \item Co-led a group of students through the process of starting a mock
        non-profit group.
  \end{innerlist}
  \item[] \textit{Reader}%
    \hfill \textbf{September 2006 to December 2006}
  \begin{innerlist}
    \item Graded mechanical design assignments (EME 150B).
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.tudelft.nl}{\textbf{Delft University of Technology}}, Delft, Zuid-Holland Netherlands
\begin{outerlist}
  \item[] \textit{Fulbright Visiting Scholar and Researcher}%
        \hfill \textbf{August 2008 to August 2009}
  \begin{innerlist}
    \item Mentored undergraduate students in their senior design projects.
  \end{innerlist}
\end{outerlist}

\section{Academic Service}
%
\begin{innerlist}
  \item Volunteer instructor for Software Carpentry
  \item Co-organizer of Cleveland's ``North Coast Biomechanics and Brew'' group
    (2014).
  \item Served on the scientific committee for the 2013 Bicycle and Motorcycle
    Dynamics Conference.
  \item Organized and mentored for five Google Summer of Code (Python Software
    Foundation/SymPy/PyDy).
  \item Organized and co-chaired both an invited and special session on single
    track vehicle dynamics at the 2012 ASME DSCC conference.
\end{innerlist}

\section{Article Reviews}
%
\begin{innerlist}
  \item Reviewed ``The effect of tyre and rider properties on the stability of a
    bicycle'' by Bulsink, Vera, et. al, for Advances in Mechanical Engineering,
    2015.
  \item Reviewed ``Changing the bicycle seat height: Effects on rider
    control.'' for the European Journal of Sports Sciences, 2015.
  \item Reviewed ``Gyro device for bicycle handling assessment: A reliability
    study'' by Fonda, Borut, et. al for the Journal of Applied Biomechanics,
    2015.
  \item Reviewed ``On the influence of tyre and rider properties on the
    stability of a bicycle.'' by Vera Bulsink, et. al, for Vehicle System
    Dynamics, 2014.
  \item Reviewed ``Are subject-specific musculoskeletal models robust to the
    uncertainties in parameter identification?'' by Giordano Valente, et. al
    for PLoS One, 2014.
  \item Reviewed four papers for the Bicycle and Motocycle Dynamics Conference
    2013 proceedings, July 2013.
  \item Reviewed ``Experimental and Numerical Analysis of Rider Motion in Weave
    Conditions'' Doria, Alberto, et. al for Vehicle System Dynamics, 2011.
\end{innerlist}

\section{Tutorials and Workshops}
%
\textbf{UCI Data Science Initiative} Irvine, California, USA
\begin{outerlist}
  \item[] \textit{ Software Carpentry Workshop}
    \hfill \textbf{February~21--22,~2015}
\end{outerlist}

\blankline

\textbf{SCIPY 2014}, Austin, Texas, USA
\begin{outerlist}
  \item[] \textit{Dynamics and Control with Python}
    \hfill \textbf{July~6,~2014}
\end{outerlist}

\blankline

\textbf{PYCON 2014}, Montreal, Quebec, Canada
\begin{outerlist}
  \item[] \textit{Dynamics and Control with Python}
    \hfill \textbf{April~9,~2014}
\end{outerlist}

\blankline

\textbf{MASB 2014}, Akron, Ohio, USA
\begin{outerlist}
  \item[] \textit{Simulation and Control of Biomechanical Systems with Python}
    \hfill \textbf{March~9,~2014}
\end{outerlist}

\section{Invited Talks}

\textbf{TU Delft}, Delft, Netherlands
\begin{outerlist}
\item[]
  \href{http://www.moorepants.info/presentations/2014/tu-delft-robotics-talk-2014}{\textit{Identification
  of human control during walking}}
    \hfill \textbf{June~6,~2014}
\end{outerlist}

\blankline

\textbf{U.S. Bicycling Hall of Fame}, Davis, CA
\begin{outerlist}
\item[] \textit{\href{http://mae.ucdavis.edu/~biosport/bhoftalk/}{How We Ride
  Bikes}} with Luke Peterson, Mont Hubbard, and Ron Hess
    \hfill \textbf{October~19,~2011}
\end{outerlist}

\blankline

\textbf{UCD Tahoe Environmental Research Center}, Lake Tahoe, NV
\begin{outerlist}
  \item[] \textit{How We Ride Bikes} with Luke Peterson and Mont Hubbard \hfill
    \textbf{May~12,~2011}
\end{outerlist}

\blankline

\textbf{Fulbright FAST Conference}, San Francisco, CA
\begin{outerlist}
  \item[] \textit{Bicycling in the Netherlands and Europe, policies and
    practices: What can America learn from them.}
    \hfill \textbf{March~12,~2010}
\end{outerlist}

\blankline

\textbf{UC Davis D-Lab}, Davis, CA
\begin{outerlist}
  \item[] \textit{Use of Human Power in the Developing World}
    \hfill \textbf{January~31,~2013, January~31,~2012, January~25,~2011, January~26,~2010}
\end{outerlist}

\blankline

\textbf{TU Delft Mechanics Colloquium}, Delft, Netherlands
\begin{outerlist}
  \item[] \textit{A First Look at Rider Biomechanics while Controlling a Bicycle}
    \hfill \textbf{June~4,~2009}
\end{outerlist}

\section{Talks}

\textbf{Cleveland State University Human Motion and Control Seminar}, Cleveland, Ohio, USA
\begin{outerlist}
\item[]
  \href{http://www.moorepants.info/presentations/2014/csu-fall-hmc-seminar}{\textit{Reproducible
    Scientific Computing with Open Software and Open Data}}
    \hfill \textbf{September~17,~2014}
\end{outerlist}

\blankline

\textbf{2014 NCSSR Visiting Scholar Kickoff}, Stanford, California, USA
\begin{outerlist}
\item[]
  \href{http://www.moorepants.info/presentations/2014/ncssr-kickoff}{\textit{Indirect
      identification of human control during walking}}
    \hfill \textbf{July~15,~2014}
\end{outerlist}

\blankline

\textbf{Dynamic Walking 2014}, Zurich, Switzerland
\begin{outerlist}
\item[]
  \href{http://www.moorepants.info/presentations/2014/DW2014}{\textit{Identification
  of human control during walking}}
    \hfill \textbf{June~10,~2014}
\end{outerlist}

\blankline

\textbf{MASB 2014}, Akron, Ohio, USA
\begin{outerlist}
\item[] \textit{Identification of human control during walking}
    \hfill \textbf{November~13,~2013}
\end{outerlist}

\blankline

\textbf{BMD 2013}, Narashino, Chiba, Japan
\begin{outerlist}
  \item[] \textit{Methods for Elimination of Crosstalk and Inertial Efects in
    Bicycle and Motorcycle Steer Torque Estimation}
    \hfill \textbf{November~13,~2013}
\end{outerlist}

\blankline

\textbf{BMD 2013}, Narashino, Chiba, Japan
\begin{outerlist}
  \item[] \textit{Identification of Open Loop Dynamics of a Manually Controlled
    Bicycle-Rider System}
    \hfill \textbf{November~11,~2013}
\end{outerlist}

\blankline

\textbf{SciPy 2013}, Austin, Texas, USA
\begin{outerlist}
  \item[] \textit{Estimating and Visualizing the Inertia of the Human Body with
    Python}
    \hfill \textbf{June~27,~2013}
\end{outerlist}

\blankline

\textbf{SciPy 2013}, Austin, Texas, USA
\begin{outerlist}
  \item[] \textit{Dynamics with SymPy Mechanics}
    \hfill \textbf{June~27,~2013}
\end{outerlist}

\blankline

\textbf{ASME DSCC 2012}, Fort Lauderdale, Florida, USA
\begin{outerlist}
  \item[] \textit{The Future of Bicycle and Motorcycle Dynamics}
    \hfill \textbf{October~18,~2012}
\end{outerlist}

\blankline

\textbf{Velo-city Global 2012}, Vancouver, British Columbia, Canada
\begin{outerlist}
  \item[] \textit{Time and Energy Penalties of Squiggly Bike Routes} with Ted
    Buehler
  \hfill \textbf{June~28,~2012}
\end{outerlist}

\blankline

\textbf{MAE Exit Seminar}, Davis, CA, USA
\begin{outerlist}
  \item[] \textit{\href{http://youtu.be/oKbaHCGK94E}{Human Control of a
    Bicycle}}
  \hfill \textbf{May~15,~2012}
\end{outerlist}

\blankline

\textbf{UCD ITS Seminar}, Davis, CA
\begin{outerlist}
\item[]
  \textit{\href{http://www.its.ucdavis.edu/?seminar=october-23-2009}{Bicycling
    in the Netherlands and Europe, policies and practices: What can America
    learn from them.}} with Eva Heinen
    \hfill \textbf{October~23,~2009}
\end{outerlist}

\blankline

\textbf{UCD MAE Seminar}, Davis, CA
\begin{outerlist}
  \item[]
    \textit{\href{http://archive.org/details/AFirstLookAtRiderBiomechanicsWhileControllingABicycle}{A
      First Look at Rider Biomechanics while Controlling a Bicycle}}
    \hfill \textbf{October~29,~2009}
\end{outerlist}

\blankline

\textbf{UCD MAE Qualifying Exam}, Davis, CA
\begin{outerlist}
  \item[] \textit{Human Control of a Bicycle}
    \hfill \textbf{October~9,~2009}
\end{outerlist}

\blankline

\textbf{ASME IDETC/CIE 2009}, San Diego, CA
\begin{outerlist}
  \item[] \textit{A Method for Estimating the Physical Properties of a Combinded Bicycle and
Rider}
    \hfill \textbf{August~31,~2009}
\end{outerlist}

\blankline

\textbf{Mulitbody Dynamics 2009}, Warsaw, Poland
\begin{outerlist}
  \item[] \textit{Rider Motion Identification During Normal Bicycling By Means of Principal
Component Analysis}
    \hfill \textbf{July~1,~2009}
\end{outerlist}

\blankline

\textbf{Fulbright Mid Year Presentation}, Amsterdam, Netherlands
\begin{outerlist}
  \item[] \textit{Jason Moore, In The Netherlands\ldots}
    \hfill \textbf{February~5,~2009}
\end{outerlist}

\blankline

\textbf{ISEA 2008}, Biarritz, France
\begin{outerlist}
  \item[] \textit{Parametric Study of Bicycle Stability}
    \hfill \textbf{June~6,~2008}
\end{outerlist}

\section{Professional Experience}
%
\href{http://www.odu.edu}{\textbf{Old Dominion University}}, Norfolk, Virginia USA
\begin{outerlist}
  \item[] \textit{Langley Full Scale Tunnel Design Engineer}%
    \hfill \textbf{June 2004 to August 2005}
  \begin{innerlist}
    \item Extensive design, modeling and drafting with Autodesk Inventor.
    \item Designed a portable floor system for a car balance.
    \item Designed a six degree of freedom full scale car balance.
    \item Wrote stress analysis reports for NASA specifications.
    \item Test-model design, fabrication and repair.
    \item Support in daily activities (test preparation, taking data, etc.).
  \end{innerlist}

  \item[] \textit{Maglev Tram Design Engineer}%
    \hfill \textbf{May 2004 to January 2005}
  \begin{innerlist}
    \item Created a reference CAD model of a
      \href{http://ww2.eng.odu.edu/maglev/}{full-scale magnetic levitation
      train car} using AutoCAD Mechanical Desktop.
  \end{innerlist}

  \item[] \textit{ODU HPV Team Project Lead}%
    \hfill \textbf{September 2003 to January 2005}
  \begin{innerlist}
    \item Lead and managed a
      \href{http://www.lions.odu.edu/~dlandman/hpv/}{mechanical engineering
      senior design project}.
    \item Designed and constructed a human powered land vehicle.
    \item Focused on bicycle frame, controls, stability, and drive train design
    \item Received 6th place out of 20 as a rookie team at the ASME Human
        Powered Vehicle Challenge.
    \item \href{http://www.lions.odu.edu/~dlandman/hpv/}{Website} designer
      and maintainer.
  \end{innerlist}

  \item[] \textit{ODU SAE Formula Team Design Engineer}%
    \hfill \textbf{2001 to 2002}
  \begin{innerlist}
    \item Helped design and fabricate a scaled formula race car.
    \item Extensive design, modeling and drafting with AutoCAD Mechanical Desktop.
    \item Designed and fabricated the drive train and composite body.
    \item Website designer.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.bauercomp.com/}{\textbf{Bauer Compressors}}, Norfolk, Virginia
USA
\begin{outerlist}
  \item[] \textit{Mechanical Design Engineer Intern}%
    \hfill \textbf{June 2003 to December 2003}
  \begin{innerlist}
    \item Extensive 3D modeling with Autodesk Inventor: modeled complex
        air compressor systems.
    \item Sheet metal design and fabrication.
    \item V-belt drive designs.
    \item Oil filtration system design.
    \item Designed parts and prepared drawings for fabrication.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.areaaccess.com/}{\textbf{Area Access}}, Norfolk, Virginia USA
\begin{outerlist}
  \item[] \textit{Elevator Mechanic Assistant}%
    \hfill \textbf{May 2002 to August 2002}
  \begin{innerlist}
    \item Installed and repaired elevators and various accessibility machines.
    \item Exposed to various electrical and mechanical systems.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.dcc.vccs.edu/}{\textbf{Danville Community College}}, Danville, Virginia USA
\begin{outerlist}
  \item[] \textit{CNC Mill Operator}%
    \hfill \textbf{June 2001 to August 2001}
  \begin{innerlist}
    \item Learned G-code/Manual Programming.
    \item Learned FeatureCam 3D CAD/CAM software.
    \item Programmed and operated a HAAS 3-axis mill.
  \end{innerlist}
\end{outerlist}

\blankline

\href{}{\textbf{Mark D. Moore Construction Company}}, 
Danville, Virginia USA
\begin{outerlist}
  \item[] \textit{Carpenter}%
    \hfill \textbf{1995 to 2001}
  \begin{innerlist}
    \item Residential house construction
    \item Framing, finishing, painting, drywall, hardwood floors, masonry
  \end{innerlist}
\end{outerlist}

\section{Volunteer Service}
%
\href{http://www.davisbikecollective.org}{\textbf{Davis Bike Collective}},
Davis,CA USA
\begin{outerlist}
  \item[] \textit{Bicycle Mechanic, Teacher and Organizer}%
    \hfill \textbf{September 2005 to June 2013}
  \begin{innerlist}
    \item Volunteered bi-weekly as a teaching mechanic.
    \item Co-founded a consensus based non-profit.
    \item Co-wrote bylaws and setup the legal non-profit.
    \item Raised thousands of dollars in donations and grants.
    \item Organized conferences, parties, fundraisers, bike rides, work parties,
      outreach events.
    \item Organized two 1500+ attendee beer tasting and movie events with New Belgium
      Brewery.
    \item Web site maintenance, shift scheduling, handled distributor orders,
      managed email listservs.
    \item Lead the workshop series ``Open Bike Night'' for one year.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.davisbicycles.org}{\textbf{Davis Bicycles!}}, Davis, CA USA
\begin{outerlist}
  \item[] \textit{Volunteer}%
    \hfill \textbf{September 2009 to June 2013}
  \begin{innerlist}
    \item Administer the organization's websites
      \href{http://www.davisbicycles.org}{[1]} and
      \href{http://www.bikedavis.info}{[2]}.
    \item Lobby city council for bicycle amenities.
    \item Worked directly with city staff on various projects.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.mayapedal.org/}{\textbf{Maya Pedal}}, San Andres Itzapa, Guatemala
\begin{outerlist}
  \item[] \textit{Volunteer Engineer}%
    \hfill \textbf{Summer 2007}
  \begin{innerlist}
    \item Constructed pedal powered machines (i.e. blender, corn
      dekerneler/grinder, etc).
    \item Design work on a macadamia nut sheller.
    \item Repaired bicycles.
    \item Shop organization: tool boards, bike graveyard.
  \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.whirlwindwheelchair.org/}{\textbf{Whirlwind Wheelchair
International}}, Lusaka, Zambia
\begin{outerlist}
  \item[] \textit{Volunteer Engineer}%
    \hfill \textbf{Summer 2006}
  \begin{innerlist}
    \item Worked at the \href{http://www.disacare.org.zm/}{Disacare Wheelchair
      Center}.
    \item Worked on the design and fabrication team for a bicycle ambulance
      trailer.
    \item Fixture design and training.
  \end{innerlist}
\end{outerlist}

\blankline

{\textbf{Virginia Beach Public Schools}}, Virginia Beach, VA
\begin{outerlist}
  \item[] \textit{Volunteer Mentor}%
    \hfill \textbf{2004}
  \begin{innerlist}
    \item Assisted high schools students with an engineering design competition.
  \end{innerlist}
\end{outerlist}

\blankline

{\textbf{UC Davis Institute for Transportation Engineers}}, Davis, CA
\begin{outerlist}
  \item[] \textit{Tour Leader}%
    \hfill \textbf{December 2006}
  \begin{innerlist}
    \item Organized a group bicycle ride and museum tour.
  \end{innerlist}
\end{outerlist}

\blankline

{\textbf{ODU College of Engineering}}, Norfolk, VA
\begin{outerlist}
  \item[] \textit{Tour Guide}%
    \hfill \textbf{February 2004}
  \begin{innerlist}
    \item Led open house tours for middle school children.
  \end{innerlist}
\end{outerlist}

\blankline

{\textbf{Davis Bicycle Commission}}, Davis, CA
\begin{outerlist}
  \item[] \textit{Bicycle Counter}%
    \hfill \textbf{}
  \begin{innerlist}
    \item Participated in bicycle usage data collection.
  \end{innerlist}
\end{outerlist}

\section{Fabrication Skills}
% this needs more detail on my other skills obtained in college
Extensive machining and fabrication experience: milling, turning, welding (MIG,
TIG, ARC, Torch, Brazing), wood working, sheet metal work

\section{Software Proficiencies}
%
Extensive drafting, solid modeling, CAD, CAM, and FEA experience. Proficient
in: CADKEY, AutoCAD, AutoCAD Mechanical Desktop, Autodesk Inventor, FeatureCAM
3D, IntelliCAD, PATRAN/NASTRAN, PRO-Engineer/PRO-Mechanica, GMAX, CNC/G-code

\blankline

Programming Languages: \href{http://www.python.org}{Python},
\href{http://www.mathworks.com/products/matlab/}{\textsc{Matlab}}, R, BASH, C,
C++, Lua, Javascript

\blankline

Web development: HTML, CSS, Javascript, Hyde, Sphinx, Flask, Amazon Web
Services, Ubuntu Server, Apache, NGinx, \href{http://www.plone.org}{Plone},
Wordpress, Joomla, Homesite, Microsoft Front Page, Macromedia Dreamweaver

\blankline

Websites that I administer:
\href{http://moorepants.info}{moorepants.info},
\href{http://clevelandwiki.org}{clevelandwiki.org},
\href{http://hmc.csuohio.edu}{hmc.csuohio.edu},
\href{http://biosport.ucdavis.edu}{Sports Biomechanics Lab},
\href{http://smartdrive.ucdavis.edu}{smartdrive.ucdavis.edu},
\href{http://drive5.us}{drive5.us},
\href{http://www.bikedavis.info}{BikeDavis.info},
\href{http://www.nstreetcohousing.org}{N Street Cohousing},
\href{http://www.davisbikecollective.org}{Davis Bike Collective},
\href{http://www.lions.odu.edu/~dlandman/hpv/}{ODU HPV},
\href{http://mae.ucdavis.edu/~biosport/jkm}{moorepants}.

\blankline

Dynamics and Simulation: SymPy Mechanics, SciPy,
\href{http://www.mathworks.com/products/matlab/}{\textsc{Matlab}}/\href{http://www.mathworks.com/products/simulink/}{Simulink},
Working Model, Autolev, Axl/CampG, Opensim, Simbody

\blankline

Computational:
SciPy, NumPy, R, Uncertainties, Pandas, Cython,
\href{http://www.mathworks.com/products/matlab/}{\textsc{Matlab}}, MathCAD


\blankline

Instrumentation: National Instruments products including
\href{http://www.ni.com/}{LabVIEW}, MatLab DAQ Toolbox, Serial Protocols

\blankline

Data: HDF5, PyTables, MySQL, MongoDB

\blankline

Graphics: Matplotlib, R,
\href{http://www.mathworks.com/products/matlab/}{\textsc{Matlab}}, GIMP,
Inkscape, Paint Shop Pro, Macromedia Fireworks, Blender, GMAX

\blankline

Operating Systems: Linux (Ubuntu and other distros), Microsoft Windows (3.1-7),
DOS

\blankline

Utilities: FTP, Version Control (Git/Mercurial/Subversion), SSH, BASH

\blankline

Reference management: B\textsc{ib}\TeX{}, JabRef, Zotero, Mendeley, Endnote

\blankline

Word processing: Vim, \LaTeX{}, Google Docs, LibreOffice, TeXnic Center,
Microsoft Office
%
\section{References}
%
\begin{outerlist}
  \item[] Academic Research
    \begin{innerlist}
      \item Dr. Antonie J. van den Bogert
        \emph{Post Doctoral Supervisor}
        Professor,
        Cleveland State University,
        Mechanical Engineering Department,
        1960 E. 24th St., SH 232
        Cleveland, Ohio 44115,
        +01-216-687-5329,
        a.vandenbogert@csuohio.edu
      \item Dr. Mont Hubbard,
        \emph{MSc and PhD advisor},
        Professor,
        University of California, Davis,
        Mechanical and Aerospace Engineering Department,
        One Shields Avenue, Davis, CA 95616,
        +01-530-752-6450,
        mhubbard@ucdavis.edu
      \item Dr. Ronald Hess,
        \emph{PhD advisor},
        Professor,
        University of California, Davis,
        Mechanical and Aerospace Engineering Department,
        One Shields Avenue, Davis, CA 95616,
        +01-530-752-1513,
        rahess@ucdavis.edu
      \item Dr. Arend Schwab,
        \emph{Fulbright and PhD advisor},
        Professor,
        Delft University of Technology,
        Mekelweg 2, NL 2628 CD Delft, The Netherlands,
        +31 15 27 82701,
        a.l.schwab@tudelft.nl
      \item Dr. Luke Peterson,
        \emph{Colleague at UCD},
        dlpeterson@ucdavis.edu
      \item Dr. Jodi Kooijman,
        \emph{Colleague at TU Delft},
        jodikooijman@gmail.com
    \end{innerlist}
  \item[] Teaching
    \begin{innerlist}
      \item Dr. Jim Schaaf,
        \emph{TA and Lecturer supervisor},
        Lecturer,
        University of California, Davis,
        Mechanical and Aerospace Engineering Department,
        One Shields Avenue, Davis, CA 95616,
        +01-530-752-5548,
        jas@ucdavis.edu
      \item Dr. Rida Farouki,
        \emph{TA supervisor},
        Professor,
        University of California, Davis,
        Mechanical and Aerospace Engineering Department,
        One Shields Avenue, Davis, CA 95616,
        +01-530-752-1779,
        farouki@ucdavis.edu
    \end{innerlist}
  \item[] Engineering
    \begin{innerlist}
      \item Dr. Tai Stillwater,
        \emph{SmartDrive and Pedal Desk},
        Postdoctoral Researcher,
        Institute of Transportation Studies,
        University of California, Davis,
        2028 Academic Surge, One Shields Avenue, Davis, CA, 95616,
        tstillwater@ucdavis.edu
      \item Matthew Seitzler, P.E. \emph{Colleague},
        Professional Engineer, at Davis Energy Group, Davis, CA,
        matt@sre-engineering.com
      \item Dr. Drew Landman,
        \emph{LFST supervisor and undergraduate mentor},
        Professor,
        Old Dominion University,
        Mechanical and Aerospace Engineering,
        1311 Engr and Comp Sci Bldg, Norfolk, VA 23529,
        +01-757-683-6008,
        dlandman@odu.edu
      \item Dr. Anthony Passerini,
        \emph{Cell shearing project supervisor},
        Assistant Professor,
        University of California, Davis,
        Biomedical Engineering Department,
        One Shields Avenue, Davis, CA 95616,
        +01-530-754-6715,
        agpasserini@ucdavis.edu
      \item John Dwyer,
        \emph{Bauer Compressors supervisor},
        Engineer Department Manager,
        john.dwyer@bauercomp.com
    \end{innerlist}
  \item[] Community Organizing
    \begin{innerlist}
      \item Dr. Robb Davis,
        \emph{colleague at Davis Bicycles!},
        Davis, CA,
        robbathome@gmail.com
      \item Dr. Sarah McCullough,
        \emph{colleague at the Davis Bike Collective},
        UC San Diego,
        smcc@ucdavis.edu
    \end{innerlist}
\end{outerlist}
%
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

